---
title: "Problem 1"
subtitle: "HW1"
author: "Hanyuan Chi(chixx105), Zhi Shen(shenx704)"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: pdf_document
---

```{r}
suppressPackageStartupMessages({
  library(ggplot2)
  library(dplyr)
})
```

# Inverse-Transform Sampling

## Question 1

Please simulate 2000 random samples from the distribution with the following CDF
$$
F(x) = 
\begin{cases}
1-e^{-x^2}\quad\mbox{ if }x\ge 0\\
0,\quad\mbox{ otherwise}
\end{cases}
$$

* Hints:
    - This question is easier since I provided a CDF to you right away
    - This is a special case of Weibull distribution
        * You will use this (type of a) distribution frequently if you do survival analysis and model "time till death" kind of scenarios.

* Output:
    - Please create a *data.frame* `df1` that contains numeric vector `df1$X` with the generated sample
    - Your file should knit in less than 1 minute
    

```{r}
N <- 2000L
set.seed(123456) # PLEASE DO NOT CHANGE THE SEED


# Please write your code below
df1 <- data.frame(u = runif(N)) %>%
      mutate(X = sqrt(-log(1-u)))

```

## Question 2

Please simulate 2000 random samples from the distribution with the following PDF
$$
f(x) =
\begin{cases}
3x^2 e^{-x^3}\quad\mbox{ if }x\ge 0\\
0,\quad\mbox{ otherwise}
\end{cases}
$$


* Hints:
    - Note that this time I gave your a PDF not a CDF

* Output:
    - Please create a *data.frame* `df2` that contains numeric vector `df2$X` with the generated sample
    - Your file should knit in less than 1 minute

```{r}
N <- 2000L
set.seed(123456) # PLEASE DO NOT CHANGE THE SEED

# Please write your code below
df2 <- data.frame(u = runif(N)) %>%
      mutate(X = (-log(1-u))^(1/3))
```


## Question 3

Please verify that your solution for Question 1 is correct by plotting:

* the empirical CDF versus true CDF
* QQPlot of sample quantiles versus true quantiles


Hints:

* Take a look at Workday1

```{r}
p1 <- ggplot(data = df1) +
  stat_ecdf(aes(x = X)) +
  stat_function(aes(x= X),
                fun = function(x) (1-exp(-x^2)),color = 'red')
p1

p2 <- ggplot(df1) +
  stat_qq(aes(sample = X),
          distribution = function(p) sqrt(-log(1-p))) +
  xlab("Theoretical Quantiles") + ylab("Sample Quantiles")
p2

```

## Question 4

Please verify that your solution for Question 2 is correct by plotting the histogram of the random outcomes versus true PDF

Hints:

* Take a look at Workday1

```{r}
p3 <- ggplot(data = df2) +
  geom_histogram(aes(x=X, y=..density..),bins = 25) +
  stat_function(aes(X), fun = function(x) (3*x^2*exp(-x^3)), color = 'red')
  
p3
```